 
%\documentclass[review]{elsarticle}
\documentclass[final,twocolumn]{elsarticle}
%\documentclass[final,5p,times,twocolumn]{elsarticle}

\usepackage{project}

\input{acronyms.tex}

\begin{document}

    \input{Questions/1-titleAbstract}

    \input{Questions/2-introduction}

    \input{Questions/3-methodology}

    \input{Questions/4-results}
%    \newpage
    \input{Questions/5-Draft}
    
\section*{\#TODO:}
\begin{enumerate}[(1)]

\item You want to focus on temporal information, and how it will help.\\
\item add more to lead the reader into the next section. The project has not been "introduced".\\
\item Aren't they both time-series?  Are you just referring to the method that they are stored?   An array of images over time (video) is still a time series.\\ 
\item You should show them as separate frames; how can you show the temporal aspects better?\\
\item But these are just spatial features plotted over time? What are the proposed temporal features? \\
\item Are you only thinking about within cycle information?  What about inter-stride information?  (for example, inter-stride variability is a well known gait feature).\\
\item Have you explored relationships between pixels/features over time?
\item With what features? Costilla-Reyes et al. [17] extracted five features
\item Does Costilla-Reye's work deserve a bit more discussion?  Is that the current state-of-the-art?
\item This seems like it doesn't fit here.  Is this specific to gait?  Explain  
\item Are you sure?!  I believe that each frame has the [x,y] position of the center of the box.  We will need to get an answer for this soon as it changes what you can do.(inter-stride)
\item Focus on what is important; where is the temporal information going to come from?  Time series of spatial information?  Temporal features?  Temporal algorithms applied to spatial features?  Are the features only within stride, or are your features going to be inter-stride?
\item Is this the main benefit? (No)
\item Why does the fact that there are multiple samples mean you want to find temporal features (the first part of the sentence doesn't "cause" the second).
\item What do you mean "find one based on speed"?  Do you mean a different one depending on which speed?  I think you (should) mean designing a system that works for all speeds. 
\item This is still to "general" for a proposal.  It doesn't give me a good idea of what you are hoping to do.
\end{enumerate}    
    
%\nolinenumbers
\bibliography{references}
 



\onecolumn
\appendix
\section{List of features}
The list of features from different categories used in this project (Table \ref{tab:Features_list}):

\input{manuscript/src/tables/project/2_features_list.tex}
\end{document}